Analysis of the inference of ratings and rankings on Higher Order Networks with complex topologies

### 2025-09-05 draft/draft.tex
progress

Thanks to the notion of orientation, a boundary linear operator $\partial:C\to C$ can be defined by its action on the vectors of the canonical basis, i.e. by
$$
\partial e_{i_0...i_k}
=
\sum_{j=0}^k
(-1)^j
e_{i_0...i_{j-1}i_{j+1}...i_k}
$$
for any $e_{i_0...i_k}\in C$.
Note that $\partial(C_k) \subseteq C_{k-1}$, where $C_{-1}=\{0\}$ denotes the trivial subspace of $C$ of dimension 0.

Since the application of any cochain $f$ to any chain $c$ is a bilinear form, the coboundary linear operator $d:C^*\to C^*$ is univocally defined by the relation
$$
df(c) = f(\partial c)
$$
for any $f\in C^*$ and $c\in C$.
Note, $d(C_k^*)\subset C_{k+1}^*$ where $C_3^*=\{0\}$ denotes the trivial subspace of $C^*$ of dimension 0.

Since the inner products on $C$ and $C^*$ are also bilinear forms, then the dual boundary $\partial^*:C\to C$ and the dual coboundary $d^*:C^*\to C^*$ linear operators can be univocally defined by
$$
\partial^*c.q
=
c.\partial q
$$
and
$$
d^*f.g
=
f.d g,
$$
for any chains $c,q\in C$ and any cochains $f,g\in C^*$, respectively.
Note, $\partial^*(C_{k-1})\subseteq C_k$ and $d^*(C_{k+1}^*)\subseteq C_k^*$.

>>>>

Thanks to the notion of orientation, a boundary linear operator $\partial:C\to C$ can be defined by its action on the vectors of the canonical basis, i.e. by
$$
\partial e_{i_0...i_k}
=
\sum_{j=0}^k
(-1)^j
e_{i_0...i_{j-1}i_{j+1}...i_k}
$$
for any $e_{i_0...i_k}\in C$.
Note that $\partial(C_k) \subseteq C_{k-1}$, where $C_{-1}=\{0\}$ denotes the trivial subspace of $C$ of dimension 0.
This induces the following direct sum decomposition
$$
\partial = \partial_0 \oplus \partial_1 \oplus \partial_2
$$
where $\partial_k(C)=\partial(C_k)\subseteq C_{k-1}$ and, in particular, $\partial_0=0$.

Since the application of any cochain $f$ to any chain $c$ is a bilinear form, the coboundary linear operator $d:C^*\to C^*$ is univocally defined by the relation
$$
df(c) = f(\partial c)
$$
for any $f\in C^*$ and $c\in C$.
Note, $d(C_k^*)\subset C_{k+1}^*$ where $C_3^*=\{0\}$ denotes the trivial subspace of $C^*$ of dimension 0.
As before, this induces the following direct sum decomposition
$$
d = d_0 \oplus d_1 \oplus d_2
$$
where $d_k(C^*)=d(C_k^*)\subseteq C_{k+1}^*$ and, in particular, $d_2=0$.

Since the inner products on $C$ and $C^*$ are also bilinear forms, then the dual boundary $\partial^*:C\to C$ and the dual coboundary $d^*:C^*\to C^*$ linear operators can be univocally defined by
$$
\partial^*c.q
=
c.\partial q
$$
and
$$
d^*f.g
=
f.d g,
$$
for any chains $c,q\in C$ and any cochains $f,g\in C^*$, respectively.
Note, that $\partial^*(C_{k-1})\subseteq C_k$ and $d^*(C_{k+1}^*)\subseteq C_k^*$, indicing the follow direct sum decompositions
$$
\partial^* = \partial_0^* \oplus \partial_1^* \oplus \partial_2^*
$$
and
$$
d^* = d_0^* \oplus d_1^* \oplus d_2^*
$$
where $\partial_k^*(C)=\partial^*(C_{k-1})\subseteq C_k$ and $d_k^*(C^*)=d(C_{k+1}^*)\subseteq C_k^*$.
